\documentclass[10pt,letterpaper]{article}
\begin{document}
\title{Research About Human Rights Reservations In Uganda}
\author{by NYONYINTONO ISAAC PITWA \\ 216004341\\  16/U/10672/PS}
\maketitle
\section{Research Problem: }
Title: An Image and video Mobile Application to reduce Human Rights Abuse in Uganda.
Image and Video Mobile Application to reduce Human Rights Abuse in Uganda.

Human rights conservation and observation have declined over the past years and  its abuse is on rapid rise and has become usual and normal behavior among the people of Uganda. its all up to the Organisation(UNHCR) to ensure human rights observation in Uganda 
However,
In response to the problem. I propose  an option for conserving human rights by using technology inform of a mobile application. 
I propose a mobile application which makes Every Ugandan watch over Another  for human rights abuse to prevent the same action from happening to him or his children or the grand children .it will ease human rights abuse reporting to the authority and guarantee immediate action to the abuser.

The citizens are offered an opportunity to either place a call or send an instant email with caption of description of the hu8man rights abuse and location attachment are within  GPS factor to reveal the location and sent to the human rights  enforcement .


\section{Objectives: }
To identify the need to intervene do something about the increased human Rights Abuse in Uganda.
To develop a mobile Application  to reduce human rights Abuse in Uganda.
To establish Technological means to analyze human rights conservation in Uganda.


\section{Basic Vs. Applied.}
The research is applied as it is intended to solve a general problem i.e. Human rights Abuse in Uganda.
\section{Descriptive Vs. Analytical.}
It is Descriptive as the research involves no evaluations  
\section{Quantitative Vs. Qualitative}
  It is Quantitative as a measure of rate of human rights analysis is to be taken during the research
\section{Conceptual VS. Empirical}
It  is Empirical as there’s a test of the research outputs to take place.


\end{document}